---
title: "homework0"
format: html
editor: visual
execute: 
  echo: false
---

# Question

(@) Write a Quarto document that defines variables $a=1, b=-1, c=-2$
and print out the solutions to $f(x) = ax^2+bx+c=0$. Do not report complex solutions, only real numbers. 

(@) Include a graph of $f(x)$ versus $x$ for $x \in (-5,5)$.

(@) Erase the PDF report and reproduce it but this time using $a=1, b=3, c=2$. 

(@) Create an HTML page with the results for this last set of values, but this time showing the code. 

# Solution
*(a)* The code applies the formula, $x=\frac{-b\pm\sqrt{b^2-4ac}}{2a}$, to solve for the quadratic equation provided.
```{r}
# Define variables
a <- 1
b <- 3
c <- 2

# Solve for quadratic equation
delta <- sqrt(b^2-4*a*c)
dummy <- c(1, -1)
x <- (-b+dummy*delta)/(2*a)
cat("The solution to the quadratic equation is ", x, ".\n")
```


*(b)* The following graph plots the function $f(x) = ax^2+bx+c=0$ for $x \in (-5,5)$, provided the $a, b,c$ values above.
```{r}
# Plot the function
xi <- seq(-5, 5, length = 300)
plot(xi, a*xi^2 + b*xi + c, type = "l", xlab = "x", ylab = "f(x)")
abline(h = 0, lty = 2)

``` 
